Himalayan Expeditions Success Analysis 

### 2024-04-14 paper/paper.qmd
Updates to multiple files (old versions so that the qmd renders as current model is not working properly)

The paper is further organized into four sections. @sec-data discusses how the dataset to be used for the analysis was obtained and pre-processed. I will explain the variables of interest in the dataset for the analysis. @sec-model describes the model being used for the analysis. @sec-results then highlights and discusses the trends and associations found during the analysis. Lastly,@sec-discussion talks about some interesting trends found in @sec-results in depth, link it to the real world and also highlight the weaknesses and future of my analysis.

@@

- $\hat{p}$ represents the probability that someone will successfully complete the peak they are on the expedition for.
- $\beta_0$ represents the intercept term of this logistical regression. It is the probability that someone will successfully complete the peak they are on the expedition for if the predictors' values are zero
- $\beta_1$ is the coefficient corresponding to height of the peak
- $\beta_2$ is the coefficient corresponding to sex of the person
- $\beta_3$ is the coefficients corresponding to age of the person
- $\beta_4$ is the coefficients corresponding to seasons of the person
- $\beta_5$ is the coefficients corresponding to if the person is attempting the summit alone.

@@

@@

# Discussion {#sec-discussion}
1) What is done in this paper? 
2) What is something that we learn about the world?
3) What are some weaknesses of what was done? What is left to learn or how should we proceed in the future?

>>>>

The paper is further organized into four sections. @sec-data discusses how the dataset to be used for the analysis was obtained and pre-processed. I will explain the variables of interest in the dataset for the analysis. @sec-model describes the model being used for the analysis. @sec-results then highlights and discusses the trends and associations found during the analysis. Lastly, @sec-discussion talks about some interesting trends found in @sec-results in depth, link it to the real world and also highlight the weaknesses and future of my analysis.

@@

- $\hat{p}$ represents the probability that someone will successfully complete the peak they are on the expedition for.
- $\beta_0$ represents the intercept term of this logistical regression. It is the probability that someone will successfully complete the peak they are on the expedition for if the predictors' values are zero
- $\beta_1$ is the coefficient corresponding to height of the peak
- $\beta_2$ is the coefficient corresponding to sex of the person
- $\beta_3$ is the coefficients corresponding to age of the person
- $\beta_4$ is the coefficients corresponding to seasons of the person
- $\beta_5$ is the coefficients corresponding to if the person is attempting the summit alone

@@

# Create a data frame with all combinations of sex and seasons
sex_levels <- unique(analysis_data$sex) 
seasons_levels <- unique(analysis_data$seasons)

new_data <- expand.grid(
  sex = sex_levels,
  seasons = seasons_levels
)

# Predicting success based on sex and seasons
predictions <- predict(expeditions_model, newdata = new_data, type = "response")

# Create a data frame to display the predictions
prediction_df <- data.frame(
  sex = new_data$sex, 
  seasons = new_data$seasons, 
  success_probability = predictions
)

@@

# Discussion {#sec-discussion}
1) What is done in this paper? 
2) What is something that we learn about the world?
